hormones

### 2019-12-02 analysis/05_DESeq2_manipulate.Rmd
new manipulation plots

a <- ggplot(mypcadf, aes(x = PC1, y = PC2, 
                         color = colData$treatment, 
                         shape = colData$tissue)) +
  geom_point(size = 2)  + 
  mytheme() +
  theme(legend.title = element_blank(), 
        axis.text = element_blank()) +
  scale_alpha_manual(values = c(0.5,1)) +
  scale_color_manual(values = colorsmanip) +
  labs(x = "PC1: 63.6% of variance", y = "PC2: 30.1% of variance")

>>>>

a <- ggplot(mypcadf, aes(x = PC1, y = PC2, 
                         color = colData$treatment, 
                         shape = colData$tissue)) +
  geom_point(size = 2)  + 
  mytheme() +
  theme(legend.title = element_blank(), 
        axis.text = element_blank()) +
  scale_alpha_manual(values = c(0.5,1)) +
  scale_color_manual(values = colorscharmaip2) +
  labs(x = "PC1: 63.6% of variance", y = "PC2: 30.1% of variance")

### 2019-12-02 analysis/07_hormones.Rmd
new manipulation plots

prolactin2 <- read_csv("../results/prolactin.csv") %>% 
          dplyr::rename("plasma_conc" = "prolactin_ng_mL",
                        "treatment" = "stage") %>% 
           dplyr::mutate(hormone = "prolactin") %>% 
           dplyr::mutate(treatment = fct_recode(treatment,
                            "m.n2" = "m.hatch",
                            "prolong" = "inc.prolong",
                            "extend" = "extend.hatch"),
                          study = fct_collapse(treatment,
                                 characterization = charlevels,
                                 manipulation = maniplevels1)) %>% 
          dplyr::select(study, treatment, sex, bird_id, hormone, plasma_conc) 
head(prolactin2)

same <- inner_join(prolactin2, prolactin, by = "bird_id")

ggplot(same, aes(x = plasma_conc.x, y = plasma_conc.y, label = bird_id)) + geom_point() + geom_text()
```

@@

```{r sexsteroids}
hormonecharplot("cort", "CORT (ng/mL)")
hormonecharplot("progesterone", "PROG (ng/mL)") 
d1 <- hormonecharplot("estradiol", "E (ng/mL)")
d2 <- hormonecharplot("testosterone", "T (ng/mL)")
plot_grid(d1,d2, nrow = 1)
```

@@

```{r manipulation}
# prolactin, removal only
hormones %>% 
    filter( hormone == c("prolactin"))  %>% 
    filter( !treatment %in% c("m.inc.d8", "prolong", "extend"))  %>% 
  ggplot(aes(x = treatment, y = plasma_conc, fill = treatment,  color = sex)) +
    geom_boxplot() + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none",
          strip.text = element_blank()) +
    scale_fill_manual(values = colorscharmaip) +
    scale_color_manual(values = sexcolors) +
    labs(y = "PRL (ng/mL)", x = NULL) +
    annotate("rect", xmin = 3.7, xmax = 5.3, ymin = -2, ymax = 0, alpha = 1) +
    annotate("rect", xmin = 5.7, xmax = 7.3, ymin = -2, ymax = 0, alpha = 1) +
    annotate("rect", xmin = 7.7, xmax = 9.3, ymin = -2, ymax = 0, alpha = 1) +
    annotate("rect", xmin = 9.7, xmax = 11.3, ymin = -2, ymax = 0, alpha = 1)

hormones %>% 
    filter( hormone == c("prolactin"))  %>% 
    filter( !treatment %in% c("m.inc.d3", "m.inc.d9", "m.inc.d17","m.n2"))  %>% 
  ggplot(aes(x = treatment, y = plasma_conc, fill = treatment,  color = sex)) +
    geom_boxplot() + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none",
          strip.text = element_blank()) +
    scale_fill_manual(values = colorscharmaip) +
    scale_color_manual(values = sexcolors) +
    labs(y = "PRL (ng/mL)", x = NULL) +
    annotate("rect", xmin = 4.7, xmax = 6.3, ymin = -2, ymax = 0, alpha = 1, alpha = 1) +
    annotate("rect", xmin = 6.7, xmax = 8.3, ymin = -2, ymax = 0, alpha = 1, alpha = 1) +
    annotate("rect", xmin = 8.7, xmax = 10.3, ymin = -2, ymax = 0, alpha = 1, alpha = 1)

  hormones %>% 
    filter( hormone %in% c(myhormone))  %>% 
  ggplot(aes(x = treatment, y = plasma_conc, fill = treatment, color = sex)) +
    geom_boxplot() + 
    mytheme() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
         # legend.position = "none",
          strip.text = element_blank()) +
    scale_fill_manual(values = colorscharmaip) +
    scale_color_manual(values = sexcolors) +
    labs(y = myylab, x = NULL) 
}

a <- hormonemanipSteroids("estradiol", "E (ng/mL)", 1)
b <- hormonemanipSteroids("testosterone", "T (ng/mL)", 3.5)
c <- hormonemanipSteroids("cort", "CORT (ng/mL)", 10)
d <- hormonemanipSteroids("progesterone", "PROG (ng/mL)",2.5)

a
b
c
d
```

>>>>

prolactin2 <- read_csv("../results/prolactin.csv") %>% 
          dplyr::rename("plasma_conc" = "prolactin_ng_mL",
                        "treatment" = "stage") %>% 
           dplyr::mutate(hormone = "prolactin") %>% 
           dplyr::mutate(treatment = fct_recode(treatment,
                            "m.n2" = "m.hatch",
                            "prolong" = "inc.prolong",
                            "extend" = "extend.hatch"),
                          study = fct_collapse(treatment,
                                 characterization = charlevels,
                                 manipulation = maniplevels1)) %>%

          dplyr::mutate(bird_id = gsub(".ATLAS", "" , bird_id)) %>% 
          dplyr::select(study, treatment, sex, bird_id, hormone, plasma_conc) 
head(prolactin2)

same <- inner_join(prolactin, prolactin2, by = "bird_id")
ggplot(same, aes(x = plasma_conc.x, y = plasma_conc.y, label = bird_id)) + geom_point() + geom_text()

all <- full_join(prolactin, prolactin2, by = "bird_id") 
onlyin1 <- anti_join(prolactin, prolactin2, by = "bird_id") 
onlyin2 <- anti_join(prolactin2, prolactin, by = "bird_id")

dim(prolactin)
dim(prolactin2)
dim(all)
dim(same)
dim(onlyin1)
dim(onlyin2)

print("only in old prolactin dataset") 
onlyin1$bird_id

print("only in new prolactin dataset") 
onlyin2$bird_id

@@

```{r manipulation}
# prolactin, removal only
hormones %>% 
    filter( hormone == c("prolactin"))  %>% 
    filter(treatment %in% c("inc.d3", "m.inc.d3", "inc.d9", "m.inc.d9", "inc.d17", "m.inc.d17", "hatch","m.n2"))  %>% 
  ggplot(aes(x = treatment, y = plasma_conc, fill = treatment,  color = sex)) +
    geom_boxplot() + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none",
          strip.text = element_blank()) +
    scale_fill_manual(values = colorscharmaip) +
    scale_color_manual(values = sexcolors) +
    labs(y = "PRL (ng/mL)", x = NULL) +
    annotate("rect", xmin = 0.6, xmax = 2.4, ymin = -2, ymax = 0, alpha = 0.25) +
    annotate("rect", xmin = 2.6, xmax = 4.4, ymin = -2, ymax = 0, alpha = 0.5) +
    annotate("rect", xmin = 4.6, xmax = 6.4, ymin = -2, ymax = 0, alpha = 0.75)  +
    annotate("rect", xmin = 6.6, xmax = 8.4, ymin = -2, ymax = 0, alpha = 1)

hormones %>% 
    filter( hormone == c("prolactin"))  %>% 
    filter( treatment %in% c("inc.d9", "m.inc.d8", "inc.d17", "prolong", "hatch", "extend", "n5"))  %>% 
  ggplot(aes(x = treatment, y = plasma_conc, fill = treatment,  color = sex)) +
    geom_boxplot() + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none",
          strip.text = element_blank()) +
    scale_fill_manual(values = colorscharmaip) +
    scale_color_manual(values = sexcolors) +
    labs(y = "PRL (ng/mL)", x = NULL) +
    annotate("rect", xmin = 0.6, xmax = 2.4, ymin = -5, ymax = -3, alpha = 0.33) +
    annotate("rect", xmin = 4.6, xmax = 5.4, ymin = -5, ymax = -3, alpha = 0.33) +
    annotate("rect", xmin = 2.6, xmax = 5.4, ymin = -2, ymax = 0, alpha = 0.66) +
    annotate("rect", xmin = 4.6, xmax = 7.4, ymin = 1, ymax = 3, alpha = 1) 
```

```{r sexsteroids}

hormonecharplot("cort", "CORT (ng/mL)")
hormonecharplot("progesterone", "PROG (ng/mL)") 
d1 <- hormonecharplot("estradiol", "E (ng/mL)")
d2 <- hormonecharplot("testosterone", "T (ng/mL)")
plot_grid(d1,d2, nrow = 1)

  hormones %>% 
    filter( hormone %in% c(myhormone))  %>% 
  ggplot(aes(x = treatment, y = plasma_conc, fill = treatment, color = sex)) +
    geom_boxplot() + 
    mytheme() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
         legend.position = "none",
          strip.text = element_blank()) +
    scale_fill_manual(values = colorscharmaip) +
    scale_color_manual(values = sexcolors) +
    labs(y = myylab, x = NULL) 
}

hormonemanipSteroids("cort", "CORT (ng/mL)", 10)
hormonemanipSteroids("progesterone", "PROG (ng/mL)",2.5)

a <- hormonemanipSteroids("estradiol", "E (ng/mL)", 1)
b <- hormonemanipSteroids("testosterone", "T (ng/mL)", 3.5)
plot_grid(a,b)

@@
